Something about Performance, 2D Component of NEMO. (TBC)

### 2015-03-09 docs/papers/nemolite2d_performance/nemolite2d_perf.tex
Added Jeremy as author

\author{H.~Lieu and J.~Holt, A.~R.~Porter, R.~Ford and G.~Riley% <-this % stops a space
\thanks{H.~Lieu and J.~Holt are with the National Oceanography Centre, Liverpool, UK.}
\thanks{A.~R.~Porter and R.~Ford are with the Science and Technology Facilities Council, UK.}% <-this % stops a space
\thanks{G.~Riley is with the University of Manchester, Manchester, UK.}% <-this % stops a space
}

@@

This work made use of the ARCHER UK National Supercomputing Service
(\url{http://www.archer.ac.uk}).

>>>>

\author{J.~Appleyard, H.~Lieu, J.~Holt, R.~W.~Ford, G.~D.~Riley and A.~R.~Porter% <-this % stops a space
\thanks{J.~Appleyard is with NVIDIA.}%
\thanks{H.~Lieu and J.~Holt are with the National Oceanography Centre, Liverpool, UK.}%
\thanks{A.~R.~Porter and R.~Ford are with the Science and Technology Facilities Council, UK.}% <-this % stops a space
\thanks{G.~Riley is with the University of Manchester, Manchester, UK.}% <-this % stops a space
}

@@

This work made use of the ARCHER UK National Supercomputing Service
(\url{http://www.archer.ac.uk}) and some {\bf NVIDIA system}.
